Epic Story 2:
As a staff member, I want to be able to view and update the status of the current orders at any point in time.

User Story 2.1:
As a staff, i should be able to log in with my username and password , so that i can access to the Gourmet Burgers system.
\bi
\item A staff is able to login successfully by providing a valid user-name and password and following successful validation be directed to the staff dashboard page
\item If the provided username or password is invalid, a suitable authentication error message must be displayed to the staff on the login page
\item If the provided username or password is empty, a suitable authentication error message must be displayed to the staff on the login page

User Story 2.2:
As a staff, i should be able to log out the system if I am already logged in so that no one else can access the system by using my computer.
\bi
\item A logged in staff should be able to be logged out his account by clicking on the log out button and taken to the Login Page

User Story 2.3:
As a staff, i should be able to view the current orders at any point in time, so that i can serve customers in a timely manner.
\bi
\item the staff should be able to click the “view orders” button to see all current orders at real time.
if the staff click into the orders, it should be able to show all the details of this order:
order number
order time
foods
username of customer
phone number of coustomer
address of customer
additional requirements 

User Story 2.4:
As a staff, i should be able to update the status of the order, so that i can manage orders more efficiently.
\bi
\item the staff should be able to click the “Pickup” button to update the status of the order.
\item Customer should be able to receive a message: “Your food is ready to pick up!” after they refresh their page.
\item The updated order should be able to disappear from staff orders menu.
